---
output: github_document
---

# shinybisonpic

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/shinybisonpic/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/shinybisonpic/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`shinybisonpic` is a Shiny app for visualizing wood bison camera trap locations and the ratios of various sex-age groups. 

## Usage

### How to Install the R Package

To install from
[GitHub](https://github.com/poissonconsulting/shinybisonpic)

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/shinybisonpic")
```

### How to Launch the App with Code

```{r, eval=FALSE}
library(shinybisonpic)
launch_shinybisonpic()
```

### How to Launch the App with RStudio Addins Button

1.  Install the package
2.  Click on the Addins drop-down and select Start shinybisonpic App

### Overview of How to Use the App

- Download template, fill with data and upload to the app
- View locations on the landscape
- Explore sex-age ratios

### User Guide

To access the user guide go to XXXX (insert link).

## bisonpic Suite

`shinybisonpic` is part of the bisonpic suite of tools. 
Other packages in this suite include:

- [bisonpictools](https://github.com/poissonconsulting/bisonpictools)
- [runbisonpic](https://github.com/poissonconsulting/runbisonpic)

## Contribution

Please report any
[issues](https://github.com/poissonconsulting/shinybisonpic/issues).

## Code of Conduct

Please note that the shinybisonpic project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
